---
title: "Corsera Assignment Practical Machine Learning"
author: "coursera student"
date: "January 2015"
output: html_document
---
We read the test and the training set:

```{r}
train = read.csv("pml-training.csv",row.names=1)
test  = read.csv("pml-testing.csv", row.names=1)
```
We exclude columns that have values missing in the test data. Also we exclude columns 2, 3 and 5 (raw timestamps and new_window) and use this smaller training set. 

```{r}
avail= !is.na(test[1,])
avail[c(2,3,5)]=F
train2=train[,avail]
```

We fit a model with generalized boosted models:

```{r, message=FALSE}
library(caret)
fitControl= trainControl(method="cv",number=3)
gbmGrid <-  expand.grid(interaction.depth = 5, n.trees = 500, shrinkage = 0.1)
gbmFit = train(classe ~ ., data=train2, method="gbm", trControl=fitControl, tuneGrid=gbmGrid)
```

We show the fit results:

```{r}
gbmFit
```

based on the gbm fit. Output probabilities, we can classify the test data

```{r}
predict(gbmFit, newdata = test, type = "prob")
```

Probabilities are all > 0.99, so we can have confidence we can predict the class labels. 


Finally we are going to write the predictions for the test set individual files, as we need them for output.

```{r}
answers=as.character(predict(gbmFit, newdata = test))

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(answers)
```
